\documentclass{article}

\usepackage[margin=0.7in]{geometry}

\title{Design Project Proposal \\ CS 111, Summer 2014}
\author{Lowell Bander, UID 204 156 534 \\
Nicole Yee, UID 403 796 037}

\begin{document}
\maketitle
	
We are interested in doing the last design project listed for Lab 1C:\\

\textit{Limit the amount of parallelism to at most N subprocesses, where N is a parameter that you can set by an argument to the shell. }\\

\textit{Currently, our implementation of Lab 1C makes as many threads as possible to parallelize. If there are X independent processes, X threads are created. In this design project, we will allow the user to dictate the maximum amount of threads that may be created to parallelize.}
\\

There are three main goals for this project. \\

\section{Set up}
\textit{Due date: July 29th} \\

The first goal is to change the code \texttt{main.c} so that it may accept an argument $N$, representing the maximum subprocesses to run in parallel. This requires changing the switch statement in main() to recognize this additional argument. The argument $N$ must also be passed to the execute command. A \texttt{README} file documenting how to execute and test this project with argument $N$ will also be included. \\

\section{Change \texttt{execute.c}}

The second milestone is to limit the amount of threads created to N in execute.c. This requires keeping a count of the number of threads created, stopping once N threads have been created. A new thread created is only after a currently running thread terminates, effectively replacing the finished thread.
\begin{enumerate}
\item Keep a counter of number of threads created and stop creating threads after N threads created.
\begin{itemize}
\item \textit{Due date: July 31st}
\end{itemize}¥
\item Restart the process of creating more threads after previous threads have completed. 
\begin{itemize}
\item \textit{Due date: August 2nd}
\end{itemize}¥
\end{enumerate}¥
\section{Test/Debug}
\textit{Due date: August 4th} \\

The last milestone is to polish the code, debugging as necessary.

\end{document}